Review of Assigned Readings

### 2018-01-04 paper/paper.tex
Update paper.tex

%************************** Chapters 3 - Econometric Modelling and Results **************************
\section{Econometric Modelling and Results}
\label{sec:EconometricModellingandResults}
As stated in the beginning, our purpose is to examine the underlying relationship between twitter buzz and bitcoin price fluctuations. From our data collection, we are left with two time series datasets representing two variables. A broadly used statistical method to simultaneously analyze multiple time series is the Vector Autoregression (VAR) approach. In this method the endogenous variables are determined both by their own historical values and by the historical values of the other endogenous variables (\cite[pp.~4--5]{luetkepohl2007new}).\\
To generate the econometric results that follow we used the statistical software STATA.

\subsection{Stationarity}
Before estimating a VAR model, the time series data must be checked for stationary. Accordingly, the means and variances are constant over time and the dataset does not show any trending behavior. Non-stationary data can lead to an inaccurate model which is undesirable. To test for stationarity, we use the Augmented Dickey-Fuller (ADF) test.\\

>>>>

%************************** Chapters 3 - Econometric Modelling and Results **************************
\section{Econometric Modelling and Results}
\label{sec:EconometricModellingandResults}
As stated in the beginning, our purpose is to examine the underlying relationship between twitter buzz and bitcoin price fluctuations. From our data collection, we are left with two time series datasets representing two variables. A broadly used statistical method to simultaneously analyze multiple time series is the Vector Autoregression (VAR) approach. In this method the endogenous variables are determined both by their own historical values and by the historical values of the other endogenous variables (\cite[pp.~4--5]{luetkepohl2007new}).\\
To generate the following econometric results we used the statistical software STATA.

\subsection{Stationarity}
Before estimating a VAR model, the time series data's stationarity must be confirmed. Namely, we need to demonstrate that the means and variances are constant over time and that the dataset does not show any trending behavior. Non-stationary data can lead to an inaccurate estimation with VAR model. To conduct stationarity test, we use the Augmented Dickey-Fuller (ADF) test.\\
